---
title: "individual-level analyses: master report"
author: "michael freund"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: spacelab
    highlight: zenburn
---

Generated from rmarkdown file: "code/indiv/_indiv.rmd".
This rmd file executes 'child' R-scripts within this directory.
These child scripts contain analysis code.
Their output is captured and 'knitted' back into this this report.
To run the code, you can either execute this .rmd file (i.e., 'knit' to html), or source each child script individually.
(These child scripts *should* be configured to run on their own.)

```{r}
t_start <- Sys.time()
```


`r knitr::spin_child('setup.R')`

# dissociation analysis

## bivariate associations

`r spin_child('bivar_superparcel.R')`

## within-region interactions (contrasts on slopes)

`r spin_child('wn_roi_contrast.R')`

## full dissociation model (4-way interaction)

`r spin_child('full_model.R')`


# model selection analysis

`r spin_child('model_selection.R')`


# arrange figure

`r spin_child('arrange_fig.R')`

```{r}
Sys.time() - t_start  ## wall-time
```
